The growth of children's semantic and phonological networks: insight from 10 languages

### 2020-04-02 journal/ms.tex
final revisins

\documentclass[english,floatsintext,man]{apa6}

\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}

% Table formatting
\usepackage{longtable, booktabs}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}

\newenvironment{lltable}
  {\begin{landscape}\begin{center}\begin{ThreePartTable}}
  {\end{ThreePartTable}\end{center}\end{landscape}}

% The following enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand\getlongtablewidth{%
 \begingroup
  \ifcsname LT@\roman{LT@tables}\endcsname
  \global\longtablewidth=0pt
  \renewcommand\LT@entry[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}%
  \@nameuse{LT@\roman{LT@tables}}%
  \fi
\endgroup}

\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            pdfauthor={},
            pdftitle={The growth of children's semantic and phonological networks: insight from 10 languages},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setlength{\parindent}{0pt}
%\setlength{\parskip}{0pt plus 0pt minus 0pt}

\setlength{\emergencystretch}{3em}  % prevent overfull lines

\ifxetex
  \usepackage{polyglossia}
  \setmainlanguage{}
\else
  \usepackage[english]{babel}
\fi

% Manuscript styling
\captionsetup{font=singlespacing,justification=justified}
\usepackage{csquotes}
\usepackage{upgreek}

 % Line numbering
  \usepackage{lineno}
  \linenumbers

\usepackage{tikz} % Variable definition to generate author note

% fix for \tightlist problem in pandoc 1.14
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Essential manuscript parts
  \title{The growth of children's semantic and phonological networks: insight
from 10 languages}

  \shorttitle{Lexical Development as Network Growth}

  \author{Abdellah Fourtassi\textsuperscript{1}, Yuan Bian\textsuperscript{2}, \& Michael C. Frank\textsuperscript{1}}

  % \def\affdep{{"", "", ""}}%
  % \def\affcity{{"", "", ""}}%

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} Department of Psychology, Stanford University\\
          \textsuperscript{2} Department of Brain and Cognitive Sciences, Massachusetts Institute of
Technology  }

  \authornote{
    Abdellah Fourtassi

@@

    Correspondence concerning this article should be addressed to Abdellah
    Fourtassi, Postal address. E-mail:
    \href{mailto:afourtas@stanford.edu}{\nolinkurl{afourtas@stanford.edu}}
  }

  \abstract{Children tend to produce words earlier when they are connected to a
variety of other words along the phonological and semantic dimensions.
Though these semantic and phonological connectivity effects have been
extensively documented, little is known about their underlying
developmental mechanism. One possibility is that learning is driven by
lexical network growth where highly connected words in the child's early
lexicon enable learning of similar words. Another possibility is that
learning is driven by highly connected words in the external learning
environment, instead of highly connected words in the early internal
lexicon. The present study tests both scenarios systematically in both
the phonological and semantic domains across 10 languages. We show that
phonological and semantic connectivity in the learning environment
drives growth in both production- and comprehension-based vocabularies,
even controlling for word frequency and length. This pattern of findings
suggests a word learning process where children harness their
statistical learning abilities to detect and learn highly connected
words in the learning environment.}
  \keywords{Word learning; semantic network; phonological network; network growth;
cross-linguistic analysis. \\

  \usepackage[sortcites=false,sorting=none]{biblatex}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\theoremstyle{definition}
\newtheorem{example}{Example}
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}

\maketitle

\setcounter{secnumdepth}{0}

\section{Introduction}\label{introduction}

What factors shape vocabulary learning over the course of early
childhood? To investigate this question, scientists have adopted
multiple research strategies, from conducting controlled laboratory
experiments (e.g. Markman, 1990) to analyzing dense corpora capturing
language learning in context (e.g., B. C. Roy, Frank, DeCamp, Miller, \&
Roy, 2015). One prominent strategy consists in documenting the timeline
of words' acquisition and studying the properties that make words easy
or hard to learn (e.g., J. C. Goodman, Dale, \& Li, 2008; Huttenlocher,
Haight, Bryk, Seltzer, \& Lyons, 1991). For example, J. C. Goodman et
al. (2008) found that, within a lexical category (e.g., nouns), higher
parental frequency is associated with earlier learning. Researchers have
studied the role of several other factors such as word length and the
mean length of utterances in which the word occurs (e.g., Braginsky,
Yurovsky, Marchman, \& Frank, 2019; Swingley \& Humphrey, 2018).

@@

While most studies have focused on the static properties of the lexical
network, a few have investigated the underlying developmental process.
In particular, Steyvers and Tenenbaum (2005) suggested that the observed
effects of connectivity are the consequence of how the lexical network
gets constructed in the child's mind. According to this explanation,
known as Preferential Attachment, highly connected words in the child's
lexicon tend to \enquote{attract} more words over time, in a
rich-get-richer scenario (Barabasi \& Albert, 1999). In other words,
what predicts learning is the \emph{internal} connectivity in the
child's early lexicon. In contrast, Hills et al. (2009) suggested that
what biases the learning is not the connectivity in the child's internal
lexicon but, rather, \emph{external} connectivity in the learning
environment. They called this alternative explanation Preferential
Acquisition. For clarity of reading, we will call preferential
attachment the Internally-driven mechanism (INT), and preferential
acquisition the Externally-driven mechanism (EXT).
Figure~\ref{fig:growth} shows an illustration of both growth scenarios
with the same simplified network.

@@

Hills et al. (2009) investigated the growth of lexico-semantic networks
in toddlers and found that growth did not proceed according to INT as
was originally hypothesized by Steyvers and Tenenbaum (2005), but rather
according to
EXT.\footnote{Besides INT and EXT, the authors tested a third mechanism (called the lure of associates) which resembles EXT in that it is driven by the connectivity of external nodes, except that this connectivity is computed with respect to words that are known. However, EXT is the externally-driven scenario that best predicted the data in this previous work.}
This is an important finding because it suggests that learning in the
early stages is mostly driven by properties of the external input,
regardless of how past knowledge is organized. However, this work
explored the INT/EXT growth in a special case: networks that were based
on 1) semantic associations, 2) production-based vocabularies, and 3)
data from English-learning children, only. The extent to which this
result depends on the domain (e.g., semantic vs.~phonological
connectivity), the vocabulary measure (production vs.~comprehension) and
culture/language is thus an open area for investigation (Hills \& Siew,
2018). In this work, we test the generality of prior findings along
these three dimensions.

@@

We adopted the following research strategy. We used parent reports on
the MacArthur-Bates Communicative Development Inventory and its
cross-linguistic adaptations (Fenson et al., 1994; Frank, Braginsky,
Yurovsky, \& Marchman, 2017). We studied the timeline of word learning
using the normative age of acquisition (i.e., the age at which at least
50\% of children know a given word). Our choice of studying the
normative learning trajectory rather than the individual trajectories
was motivated by the nature of the dataset used---which is primarily
based on cross-sectional studies. Children may vary in their individual
learning trajectories, but the aggregate data provide highly robust
measures of the average learning patterns (Fenson et al., 1994). The use
of such measures has lead to important insights on the mechanisms of
word learning (J. C. Goodman et al., 2008; Hills et al., 2010, 2009;
Stella et al., 2017; Storkel, 2009).

@@

\section{Networks}\label{networks}

\subsection{Data}\label{data}

@@

\subsection{Age of acquisition}\label{age-of-acquisition}

For each word in the CDI data, we compute the proportion of children who
understand or produce the word at each month. Then we fit a logistic
curve to these proportions and determined when the curve crosses 0.5,
i.e., the age at which at least 50\% of children know the word. We take
this point in time to be each word's age of acquisition (Braginsky et
al., 2019; J. C. Goodman et al., 2008).

@@

\caption{\label{tab:stats}Statistics for the dataset we used. The ages are in months.}
\centering
\begin{tabular}[t]{>{\bfseries}lrlrrlr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{Comprehension} & \multicolumn{3}{c}{Production} \\
\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
Language & Nouns & Ages & N & Nouns & Ages & N\\
\midrule
Croatian & 209 & 8-16 & 250 & 312 & 16-30 & 377\\
Danish & 200 & 8-20 & 2,398 & 316 & 16-36 & 3,714\\
English & 209 & 8-18 & 2,435 & 312 & 16-30 & 5,520\\
French & 197 & 8-16 & 537 & 307 & 16-30 & 827\\
Italian & 209 & 7-24 & 648 & 312 & 18-36 & 752\\
Norwegian & 193 & 8-20 & 2,922 & 316 & 16-36 & 9,303\\
Russian & 207 & 8-18 & 768 & 314 & 18-36 & 1,037\\
Spanish & 208 & 8-18 & 788 & 312 & 16-30 & 1,146\\
Swedish & 205 & 8-16 & 467 & 339 & 16-28 & 900\\
Turkish & 180 & 8-16 & 1,115 & 297 & 16-36 & 2,422\\
\bottomrule
\end{tabular}
\end{table}

\subsection{Semantic networks}\label{semantic-networks}

@@

\subsection{Phonological networks}\label{phonological-networks}

@@

\section{Analysis}\label{analysis}

\subsection{Static properties of the global
network}\label{static-properties-of-the-global-network}

@@

\subsubsection{Connectivity predicts the age of
acquisition}\label{connectivity-predicts-the-age-of-acquisition}

@@

\subsubsection{Power-law degree
distribution}\label{power-law-degree-distribution}

We also analyzed the global network's degree distribution. The shape of
this distribution is particularly relevant to INT as this growth
scenario is known to generate networks with a power-law degree
distribution, i.e., a distribution of the form
\(p(k) \propto \frac{1}{k^{\alpha}}\) (Barabasi \& Albert, 1999). If the
end-state network displays this property, this fact would suggest, but
not prove, an INT-like generative process. If, however, the degree
distribution is very different from a power law, this would
significantly weaken the case for INT. The log-log plots are shown in
Figure \ref{fig:degreeDist}. We fit a power law to each empirical degree
distribution following the procedure outlined in Clauset, Shalizi, and
Newman (2009) and using a related R package (poweRlaw, Gillespie, 2015).

@@

\caption{\label{tab:powerLawProd}Results of fitting a power law model to the degree (i.e., connectivity) distribution in each model for production data. Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis. If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.}
\centering
\begin{tabular}[t]{>{\bfseries}lrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{Phono.} & \multicolumn{3}{c}{Sem.} \\
\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
Language & cut-off & alpha & p-value & cut-off & alpha & p-value\\
\midrule
Croatian & 4 & 2.18 & 0.123 & 4 & 2.55 & 0.881\\
Danish & 11 & 4.55 & 0.858 & 4 & 2.38 & 0.001\\
English & 20 & 9.14 & 0.511 & 5 & 2.66 & 0.132\\
French & 20 & 3.75 & 0.112 & 8 & 2.81 & 0.133\\
Italian & 9 & 9.45 & 0.780 & 4 & 2.93 & 0.608\\
Norwegian & 15 & 6.28 & 0.744 & 5 & 2.88 & 0.201\\
Russian & 8 & 4.20 & 0.541 & 24 & 5.61 & 0.723\\
Spanish & 13 & 8.75 & 0.736 & 4 & 2.98 & 0.460\\
Swedish & 11 & 4.68 & 0.103 & 4 & 2.49 & 0.171\\
Turkish & 8 & 3.26 & 0.375 & 4 & 2.87 & 0.925\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:powerLawComp}Results of fitting a power law model to the degree distribution in each model for comprehension data. Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis. If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.}
\centering
\begin{tabular}[t]{>{\bfseries}lrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{Phono.} & \multicolumn{3}{c}{Sem.} \\
\cmidrule(l{2pt}r{2pt}){2-4} \cmidrule(l{2pt}r{2pt}){5-7}
Language & cut-off & alpha & p-value & cut-off & alpha & p-value\\
\midrule
Croatian & 2 & 2.06 & 0.020 & 5 & 2.67 & 0.895\\
Danish & 5 & 2.98 & 0.136 & 4 & 2.39 & 0.005\\
English & 13 & 5.16 & 0.235 & 4 & 2.64 & 0.765\\
French & 18 & 5.58 & 0.336 & 4 & 2.63 & 0.330\\
Italian & 8 & 10.27 & 0.909 & 4 & 2.88 & 0.688\\
Norwegian & 13 & 7.65 & 0.440 & 5 & 2.87 & 0.433\\
Russian & 5 & 3.97 & 0.854 & 8 & 3.91 & 0.952\\
Spanish & 5 & 3.01 & 0.085 & 5 & 3.11 & 0.552\\
Swedish & 9 & 6.75 & 0.102 & 5 & 2.81 & 0.713\\
Turkish & 9 & 5.73 & 0.958 & 4 & 3.13 & 0.887\\
\bottomrule
\end{tabular}
\end{table}

@@

\subsection{Network growth models}\label{network-growth-models}

To test the network growth scenarios, we fit two growth models to the
data. We calculated the probability that a word \(w_i\), with a utility
value \(u_i\) would enter the lexicon at a given month, using a softmax
function:

\begin{equation}
 p(w_i)= \frac{e^{\beta u_i}}{\sum_j e^{\beta u_j} }
\end{equation}

@@

We estimated the parameter \(\beta\) using a Bayesian approach. The
inference was performed using the probabilistic programming language
WebPPL (N. Goodman \& Stuhlmuller, 2014). We defined a uniform prior
over \(\beta\), and at each month, we computed the likelihood function
over words that could possibly enter the lexicon at that month, fit to
the words that have been learned at that month (using Formula 1). Markov
Chain Monte Carlo sampling resulted in a posterior distribution over
\(\beta\), which we summarized in Figure \ref{fig:growthPred}. The
results replicate Hills et al.'s original finding regarding the semantic
network in English and the production-based vocabulary, which is that
this network grows by EXT, not by INT. Crucially, our results show that,
generally speaking, this finding generalizes to comprehension-based
vocabulary, and holds across languages. This generalization was obtained
in both the semantic\footnote{One could imagine that the fact of using
  English free association norms cross-linguistically would decrease the
  effect of non-English semantic networks because of possible cultural
  differences. However, our findings do not support this assumption;
  rather, it supports our initial approximation about the shared nature
  of the semantic similarity measure. That said, this approximation is
  not perfect. For example, there is evidence that a small part of the
  variance in free association data can be explained by phonological
  similarity (Kachergis, Cox, \& Jones, 2011; Matusevych \& Stevenson,
  2018), thus leading to possibly minor cross-linguistic differences.}
and phonological domains.

@@

\subsection{Comparison to other predictors of age of
acquisition}\label{comparison-to-other-predictors-of-age-of-acquisition}

>>>>

\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={The growth of children's semantic and phonological networks: insight from 10 languages},
            pdfkeywords={Word learning; semantic network; phonological network; network growth; cross-linguistic analysis.},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{The growth of children's semantic and phonological networks: insight from 10 languages}
    \author{true \\ true \\ true}
    \date{}

% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Lexical Development as Network Growth}
\author{Abdellah Fourtassi\textsuperscript{1}, Yuan Bian\textsuperscript{2}, \& Michael C. Frank\textsuperscript{1}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Department of Brain and Cognitive Sciences, Massachusetts Institute of Technology}
\authornote{
Abdellah Fourtassi

@@

Correspondence concerning this article should be addressed to Abdellah Fourtassi, Postal address. E-mail: afourtas@stanford.edu}
\keywords{Word learning; semantic network; phonological network; network growth; cross-linguistic analysis.}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage[sortcites=false,sorting=none]{biblatex}

\abstract{
Children tend to produce words earlier when they are connected to a variety of other words along the phonological and semantic dimensions. Though these semantic and phonological connectivity effects have been extensively documented, little is known about their underlying developmental mechanism. One possibility is that learning is driven by lexical network growth where highly connected words in the child's early lexicon enable learning of similar words. Another possibility is that learning is driven by highly connected words in the external learning environment, instead of highly connected words in the early internal lexicon. The present study tests both scenarios systematically in both the phonological and semantic domains across 10 languages. We show that phonological and semantic connectivity in the learning environment drives growth in both production- and comprehension-based vocabularies, even controlling for word frequency and length. This pattern of findings suggests a word learning process where children harness their statistical learning abilities to detect and learn highly connected words in the learning environment.
}

\begin{document}
\maketitle

\#Introduction

What factors shape vocabulary learning over the course of early childhood? To investigate this question, scientists have adopted multiple research strategies, from conducting controlled laboratory experiments (e.g. Markman, 1990) to analyzing dense corpora capturing language learning in context (e.g., Roy, Frank, DeCamp, Miller, \& Roy, 2015). One prominent strategy consists in documenting the timeline of words' acquisition and studying the properties that make words easy or hard to learn (e.g., Goodman, Dale, \& Li, 2008; Huttenlocher, Haight, Bryk, Seltzer, \& Lyons, 1991). For example, Goodman et al. (2008) found that, within a lexical category (e.g., nouns), higher parental frequency is associated with earlier learning. Researchers have studied the role of several other factors such as word length and the mean length of utterances in which the word occurs (e.g., Braginsky, Yurovsky, Marchman, \& Frank, 2019; Swingley \& Humphrey, 2018).

@@

While most studies have focused on the static properties of the lexical network, a few have investigated the underlying developmental process. In particular, Steyvers \& Tenenbaum (2005) suggested that the observed effects of connectivity are the consequence of how the lexical network gets constructed in the child's mind. According to this explanation, known as Preferential Attachment, highly connected words in the child's lexicon tend to \enquote{attract} more words over time, in a rich-get-richer scenario (Barabasi \& Albert, 1999). In other words, what predicts learning is the \emph{internal} connectivity in the child's early lexicon. In contrast, Hills et al. (2009) suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, \emph{external} connectivity in the learning environment. They called this alternative explanation Preferential Acquisition. For clarity of reading, we will call preferential attachment the Internally-driven mechanism (INT), and preferential acquisition the Externally-driven mechanism (EXT). Figure~\ref{fig:growth} shows an illustration of both growth scenarios with the same simplified network.

@@

Hills et al. (2009) investigated the growth of lexico-semantic networks in toddlers and found that growth did not proceed according to INT as was originally hypothesized by Steyvers \& Tenenbaum (2005), but rather according to EXT.\footnote{Besides INT and EXT, the authors tested a third mechanism (called the lure of associates) which resembles EXT in that it is driven by the connectivity of external nodes, except that this connectivity is computed with respect to words that are known. However, EXT is the externally-driven scenario that best predicted the data in this previous work.} This is an important finding because it suggests that learning in the early stages is mostly driven by properties of the external input, regardless of how past knowledge is organized. However, this work explored the INT/EXT growth in a special case: networks that were based on 1) semantic associations, 2) production-based vocabularies, and 3) data from English-learning children, only. The extent to which this result depends on the domain (e.g., semantic vs.~phonological connectivity), the vocabulary measure (production vs.~comprehension) and culture/language is thus an open area for investigation (Hills \& Siew, 2018). In this work, we test the generality of prior findings along these three dimensions.

@@

We adopted the following research strategy. We used parent reports on the MacArthur-Bates Communicative Development Inventory and its cross-linguistic adaptations (Fenson et al., 1994; Frank, Braginsky, Yurovsky, \& Marchman, 2017). We studied the timeline of word learning using the normative age of acquisition (i.e., the age at which at least 50\% of children know a given word). Our choice of studying the normative learning trajectory rather than the individual trajectories was motivated by the nature of the dataset used---which is primarily based on cross-sectional studies. Children may vary in their individual learning trajectories, but the aggregate data provide highly robust measures of the average learning patterns (Fenson et al., 1994). The use of such measures has lead to important insights on the mechanisms of word learning (Goodman et al., 2008; Hills et al., 2010, 2009; Stella et al., 2017; Storkel, 2009).

@@

\hypertarget{networks}{%
\section{Networks}\label{networks}}

\hypertarget{data}{%
\subsection{Data}\label{data}}

@@

\hypertarget{age-of-acquisition}{%
\subsection{Age of acquisition}\label{age-of-acquisition}}

For each word in the CDI data, we compute the proportion of children who understand or produce the word at each month. Then we fit a logistic curve to these proportions and determined when the curve crosses 0.5, i.e., the age at which at least 50\% of children know the word. We take this point in time to be each word's age of acquisition (Braginsky et al., 2019; Goodman et al., 2008).

@@

\caption{\label{tab:stats}Statistics for the dataset we used. The ages are in months.}
\centering
\begin{tabular}[t]{>{\bfseries}lrlrrlr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{Comprehension} & \multicolumn{3}{c}{Production} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
Language & Nouns & Ages & N & Nouns & Ages & N\\
\midrule
Croatian & 209 & 8-16 & 250 & 312 & 16-30 & 377\\
Danish & 200 & 8-20 & 2,398 & 316 & 16-36 & 3,714\\
English & 209 & 8-18 & 2,435 & 312 & 16-30 & 5,520\\
French & 197 & 8-16 & 537 & 307 & 16-30 & 827\\
Italian & 209 & 7-24 & 648 & 312 & 18-36 & 752\\
Norwegian & 193 & 8-20 & 2,922 & 316 & 16-36 & 9,303\\
Russian & 207 & 8-18 & 768 & 314 & 18-36 & 1,037\\
Spanish & 208 & 8-18 & 788 & 312 & 16-30 & 1,146\\
Swedish & 205 & 8-16 & 467 & 339 & 16-28 & 900\\
Turkish & 180 & 8-16 & 1,115 & 297 & 16-36 & 2,422\\
\bottomrule
\end{tabular}
\end{table}

\hypertarget{semantic-networks}{%
\subsection{Semantic networks}\label{semantic-networks}}

@@

\hypertarget{phonological-networks}{%
\subsection{Phonological networks}\label{phonological-networks}}

@@

\hypertarget{analysis}{%
\section{Analysis}\label{analysis}}

\hypertarget{static-properties-of-the-global-network}{%
\subsection{Static properties of the global network}\label{static-properties-of-the-global-network}}

@@

\#\#\#Connectivity predicts the age of acquisition

@@

\#\#\#Power-law degree distribution

We also analyzed the global network's degree distribution. The shape of this distribution is particularly relevant to INT as this growth scenario is known to generate networks with a power-law degree distribution, i.e., a distribution of the form \(p(k) \propto \frac{1}{k^{\alpha}}\) (Barabasi \& Albert, 1999). If the end-state network displays this property, this fact would suggest, but not prove, an INT-like generative process. If, however, the degree distribution is very different from a power law, this would significantly weaken the case for INT. The log-log plots are shown in Figure \ref{fig:degreeDist}. We fit a power law to each empirical degree distribution following the procedure outlined in Clauset, Shalizi, \& Newman (2009) and using a related R package (poweRlaw, Gillespie, 2015).

@@

\caption{\label{tab:powerLawProd}Results of fitting a power law model to the degree (i.e., connectivity) distribution in each model for production data. Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis. If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.}
\centering
\begin{tabular}[t]{>{\bfseries}lrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{Phono.} & \multicolumn{3}{c}{Sem.} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
Language & cut-off & alpha & p-value & cut-off & alpha & p-value\\
\midrule
Croatian & 4 & 2.55 & 0.881 & 4 & 2.18 & 0.123\\
Danish & 4 & 2.38 & 0.001 & 11 & 4.55 & 0.858\\
English & 5 & 2.66 & 0.132 & 20 & 9.14 & 0.511\\
French & 8 & 2.81 & 0.133 & 20 & 3.75 & 0.112\\
Italian & 4 & 2.93 & 0.608 & 9 & 9.45 & 0.780\\
Norwegian & 5 & 2.88 & 0.201 & 15 & 6.28 & 0.744\\
Russian & 24 & 5.61 & 0.723 & 8 & 4.20 & 0.541\\
Spanish & 4 & 2.98 & 0.460 & 13 & 8.75 & 0.736\\
Swedish & 4 & 2.49 & 0.171 & 11 & 4.68 & 0.103\\
Turkish & 4 & 2.87 & 0.925 & 8 & 3.26 & 0.375\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:powerLawComp}Results of fitting a power law model to the degree distribution in each model for comprehension data. Numbers indicate the cut-off degree, the scaling parameter alpha, and the p-value which quantifies the plausibility of the power law hypothesis. If the p-value is close to 1, a power law cannot be rejected as a plausible fit for the data.}
\centering
\begin{tabular}[t]{>{\bfseries}lrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{3}{c}{Phono.} & \multicolumn{3}{c}{Sem.} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
Language & cut-off & alpha & p-value & cut-off & alpha & p-value\\
\midrule
Croatian & 5 & 2.67 & 0.895 & 2 & 2.06 & 0.020\\
Danish & 4 & 2.39 & 0.005 & 5 & 2.98 & 0.136\\
English & 4 & 2.64 & 0.765 & 13 & 5.16 & 0.235\\
French & 4 & 2.63 & 0.330 & 18 & 5.58 & 0.336\\
Italian & 4 & 2.88 & 0.688 & 8 & 10.27 & 0.909\\
Norwegian & 5 & 2.87 & 0.433 & 13 & 7.65 & 0.440\\
Russian & 8 & 3.91 & 0.952 & 5 & 3.97 & 0.854\\
Spanish & 5 & 3.11 & 0.552 & 5 & 3.01 & 0.085\\
Swedish & 5 & 2.81 & 0.713 & 9 & 6.75 & 0.102\\
Turkish & 4 & 3.13 & 0.887 & 9 & 5.73 & 0.958\\
\bottomrule
\end{tabular}
\end{table}

@@

\hypertarget{network-growth-models}{%
\subsection{Network growth models}\label{network-growth-models}}

To test the network growth scenarios, we fit two growth models to the data. We calculated the probability that a word \(w_i\), with a utility value \(u_i\) would enter the lexicon at a given month, using a softmax function:
\begin{equation}
 p(w_i)= \frac{e^{\beta u_i}}{\sum_j e^{\beta u_j} }
\end{equation}

@@

We estimated the parameter \(\beta\) using a Bayesian approach. The inference was performed using the probabilistic programming language WebPPL (Goodman \& Stuhlmuller, 2014). We defined a uniform prior over \(\beta\), and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using Formula 1). Markov Chain Monte Carlo sampling resulted in a posterior distribution over \(\beta\), which we summarized in Figure \ref{fig:growthPred}. The results replicate Hills et al.'s original finding regarding the semantic network in English and the production-based vocabulary, which is that this network grows by EXT, not by INT. Crucially, our results show that, generally speaking, this finding generalizes to comprehension-based vocabulary, and holds across languages. This generalization was obtained in both the semantic\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption; rather, it supports our initial approximation about the shared nature of the semantic similarity measure. That said, this approximation is not perfect. For example, there is evidence that a small part of the variance in free association data can be explained by phonological similarity (Kachergis, Cox, \& Jones, 2011; Matusevych \& Stevenson, 2018), thus leading to possibly minor cross-linguistic differences.} and phonological domains.

@@

\hypertarget{comparison-to-other-predictors-of-age-of-acquisition}{%
\subsection{Comparison to other predictors of age of acquisition}\label{comparison-to-other-predictors-of-age-of-acquisition}}
